Processing simulation output

### 2020-05-14 manuscript/manuscript/manuscript.Rmd
update research archive
update readme in root

<!-- Data are available via the $\texttt{ASReview}$ GitHub page^[https://github.com/asreview/systematic-review-datasets]. -->
<!-- All datasets accompanying the systematic reviews are openly published.  -->
## Datasets 
The models were simulated on a convenience sample of six systematic review datasets. The data selection process was driven by two factors. Firstly, datasets were selected based on their background, given the need for datasets from diverse research areas. Secondly, datasets were selected by their availability, given the limited timespan of the current project. Thirdly, all original data files should be openly published with a CC-BY license, and are available through the [$\texttt{ASReview}$ GitHub page](https://github.com/asreview/systematic-review-datasets).

@@

```{r}
# measures for variation within 15 runs 
#sumruns <- readRDS("../../results/output/sumruns.RDS")
# tabruns <- sumruns %>%
#   pivot_wider(names_from = dataset, values_from = c("mean_wss95","sd_wss95", "mean_wss99", "sd_wss99","mean_wss100","sd_wss100", "mean_rrf5","sd_rrf5", "mean_rrf10", "sd_rrf10", "mean_rrf20","sd_rrf20", "mean_loss", "sd_loss"))

# tabruns <- sumruns %>%
#   select(dataset, model, mean_wss95, sd_wss95, mean_rrf10, sd_rrf10, mean_loss, sd_loss) 
#

# wss95tab <- tabruns %>%
#   select(dataset, model, mean_wss95, sd_wss95) %>%
#   pivot_wider(names_from = dataset, values_from = c("mean_wss95","sd_wss95"))

# wss95tab <- stabres %>%
#   select(model, starts_with("wss.95"))

>>>>

<!-- Data are available via the $\texttt{ASReview}$ GitHub page^[https://github.com/asreview/systematic-review-datasets]. -->
<!-- All datasets accompanying the systematic reviews are openly published.  -->
## Datasets 
The models were simulated on a convenience sample of six systematic review datasets. The data selection process was driven by three factors. Firstly, datasets were selected based on their background, given the need for datasets from diverse research areas. Secondly, datasets were selected by their availability, given the limited timespan of the current project. Thirdly, all original data files should be openly published with a CC-BY license, and are available through the [$\texttt{ASReview}$ GitHub page](https://github.com/asreview/systematic-review-datasets).

@@

```{r}

### 2020-05-14 results/README.Rmd
update readme in root

---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(rjson)
library(tidyverse)
library(knitr)
```

Script for reading simulation files
```{python}
# to be found on harddrive results folder
```

Script for reading results 
```{r}
data <- readRDS("../simulation_study/R/00_datasets.RDS")
models <- list.files("/Volumes/Gerbrich/asreview/results/one/statistics/")
names(models) <- c("NB + TF-IDF", "LR + D2V", "LR + TF-IDF", "RF + D2V", "RF + TF-IDF", "SVM + D2V", "SVM + TF-IDF" )

# function that reads results for a model M 
read_results <- function(m){
   files = list.files(paste0("/Volumes/Gerbrich/asreview/results/one/statistics/", m), recursive = TRUE)
  # names of the files are the data
  names(files) <- str_split(files, "/", simplify = TRUE)[,1]
  # read data
  dat <- lapply(files, function(x) fromJSON(file = paste0("/Volumes/Gerbrich/asreview/results/one/statistics/", m, "/", x)))

@@

  return(dat)
}
```

Parse 
```{r, eval = FALSE}
dat$virus
# extract only wss, rrf, and loss values from list
test <- map(dat, `[`, c("wss", "rrf", "loss"))
# transorm into dataframe
test <- map_dfr(test, ~ as.data.frame(.x), .id = "dataset")
# add model name
test <- test %>% mutate(model = "NB + TF-IDF")
```

Apply over all datasets and models 
```{r}
# extract results for all models
# list for models separately
results <- lapply(models, read_results)

# all in one dataframe
results <- do.call("rbind", results)
results %>%
  group_by(dataset) %>%
  arrange(loss)
```

Create table
```{r}
library(tables)
library(data.table)
library(gt)
library(tidyr)
library(tidyverse)
tabres <- 
  results %>%
  pivot_wider(names_from = dataset, values_from = c("wss.95", "wss.99", "wss.100", "rrf.5", "rrf.10", "rrf.20", "loss"))

```

```{r}
library(expss)

test <- results %>% pivot_longer(cols = c(starts_with("wss"), starts_with("rrf"), "loss"), names_to = "stats", values_to = "value")

tab <- 
  test %>%
  tab_rows(model) %>%
  tab_cells(value) %>%
  tab_cols(dataset %nest% stats) %>%
  tab_stat_mean() %>%
  tab_pivot()

```

```{r}
tabres %>%
  select(model, starts_with("wss.95"), starts_with("loss"))

gtest <- tabres %>%
  gt()

gtest <- results %>%
  gt() %>%

```
```{r}
library(flextable)
typology <- data.frame(
  col_keys = names(results)[2:43],
  what = rep(data,7),
  measure = rep(c("WSS@95", "WSS@99", "WSS@100", "RRF@5", "RRF@10", "RRF@20", "ATD"), each = )
  what = c(rep("WSS", 3), rep("RRF", 3), "loss"),
  measure = c("95", "99", "100", "5", "10", "20", "0"),
  stringsAsFactors = FALSE
)

test <- flextable(tabres)
test <- set_header_df(test, mapping = typology, key = "col_keys")
merge_h(test, part = "header")
```

Now again for with seed 
```{r}
#files = list.files("/Volumes/Gerbrich/asreview/results/one/statistics/", recursive = TRUE)

```

>>>>

---
title: "Processing simulation output"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(rjson)
library(tidyverse)
library(knitr)
library(flextable)
library(officer)
```

This directory stores all files used to extract figures and statistics from the simulation study output.
The directory contains the following:

- `extract_plots.ipynb`, a jupyter notebook producing recall curves from the simulation output (Figure 1 and 2 in the manuscript)
- `extract_results.ipynb`, a jupyter notebook extracting `.json` files containing statistics from the simulation output (WSS, RRF, ATD in table 2, 3, and 4 in the manuscript)
- `one_seed`, containing all plots and data produced by the two jupyter notebooks above.
- `README.Rmd` containing R-code to transform the .json files into readable tables for the manuscript.
- `output` contains the abovementioned tables, stored as .RDS files.

## Define functions for reading simulation output 
```{r}
data <- readRDS("../simulation_study/R/00_datasets.RDS")
models <-c("BCTD", "LCDD", "LCTD", "RCDD", "RCTD", "SCDD", "SCTD")
names(models) <- c("NB + TF-IDF", "LR + D2V", "LR + TF-IDF", "RF + D2V", "RF + TF-IDF", "SVM + D2V", "SVM + TF-IDF" )

# function that reads results for all 15 runs
read_results <- function(m){
   files = list.files(paste0("one_seed/statistics/", m), pattern = "all.json", recursive = TRUE)
  # names of the files are the data
  names(files) <- str_split(files, "/", simplify = TRUE)[,1]
  # read data
  dat <- lapply(files, function(x) fromJSON(file = paste0("one_seed/statistics/", m, "/", x)))

@@

  return(dat)
}

# function for extracting all separate runs 
read_trials <- function(m){
   files <- list.files(paste0("one_seed/statistics/", m), pattern = "results_", recursive = TRUE, full.names=TRUE)
  # names of the files are the data
  names(files) <- str_split(files, "/", simplify = TRUE)[,9]

  # read data
  dat <- lapply(files, function(x) fromJSON(file = x))

  return(dat)
}

# ATD needs to be adjusted for 1 prior inclusion and 1 prior exclusion! 
# compute adjusted ATD to make it equal to the area above the curve
datastats <- readRDS("datastats.RDS") %>%
  select(Dataset, candidates_test, incl_test) %>%
  # account for 1 prior exclusion and 1 prior inclusion
  mutate(n_1 = incl_test, n_excl = candidates_test-n_1, n_1_noprior = incl_test-1, candidates_noprior = candidates_test -1) %>%
  mutate(ratio = (n_1_noprior/n_1)/(candidates_noprior/candidates_test))

datastats$dataset <- c("ace", "nudging", "ptsd", "software", "virus", "wilson")
atdratio <- datastats %>%
  select(dataset, ratio)
```

## Load results for 15 separate trials
```{r}
# read all 15 trials separately
runs <- lapply(models, FUN = read_trials)

# all in one dataframe
runs <- do.call("rbind", runs)

# convert loss (ttd) to percentage 
runs$loss <- runs$loss*100
# adjust loss to N_1 : N_1-1 (to the prior inclusions)
runs <- left_join(runs, atdratio, by = "dataset")
runs <- runs %>%
  mutate(loss = loss/ratio) %>%
  select(-ratio)

# save results file 
saveRDS(runs, "output/runs.RDS")
```

Compute standarad deviation from the 15 separate trials.
```{r}
# compute standard deviation (bootstrapped)
sdruns <- 
  runs %>%
  select(dataset, model, wss.95, rrf.10, loss) %>% 
  group_by(model, dataset) %>%
  summarise(sdwss.95 = sd(wss.95),
            sdrrf.10 = sd(rrf.10),
            sdloss = sd(loss))

saveRDS(sdruns, "output/sdruns.RDS")
```

## Load results as means over all 15 trials  
```{r}
# extract results for all models
# list for models separately
results <- lapply(models, read_results)

# all in one dataframe
results <- do.call("rbind", results)

# convert loss (ttd) to percentage 
results$loss <- results$loss*100
# adjust loss to N_1 : N_1-1
results <- left_join(results, atdratio, by = "dataset")

results <- results %>%
  mutate(loss = loss/ratio) %>%
  select(-ratio)

# save results file 
saveRDS(results, "output/results.RDS")
```

Create table for manuscript (all means over 15 runs)
```{r}
tabres <- 
  results %>%
  pivot_wider(names_from = dataset, values_from = c("wss.95", "wss.99", "wss.100", "rrf.5", "rrf.10", "rrf.20", "loss"))

# table of mean statistics over all runs 
stabres <- 
tabres %>%
  # select statistics
  select(model,
         starts_with("wss.95"),
         starts_with("rrf.10"), 
         starts_with("loss")) %>%
  # reorder datasets
  select(model,
         ends_with("nudging"),
         ends_with("ptsd"),
         ends_with("software"),
         ends_with("ace"),
         ends_with("virus"),
         ends_with("wilson")
         )

saveRDS(stabres, "output/tabresults.RDS")

knitr::kable(stabres, format = "markdown", digits = 1)
```
